\section{Review of Relevant Literature}

The ``Multi Semester Multi Cohort'' approach we describe builds on well established ideas and practices of project-based pedagogy\cite{projects}. As can be seen it carries forward every one of the five key features identified by Blumenfeld et al. in ''Inquiry in project-based science classrooms \cite{blumenfeld}'', paraphrased here:
\begin{enumerate}
    \item \textit{``Starts with a driving question, a problem to be solved"} Clearly this is the central premise of our MSMC course structure.
    \item \textit{``Students explore the driving question in authentic ways''}   This is implicit inasmuch the course is structured as a hands-on lab, where students are interacting with each other and writing and testing software on actual robots. As will be mentioned in the section on technology choice, we purposely selected both hardware and software very typically used in commercial and research contexts.
    \item \textit{``Students, teachers and community members collaborate to find solutions''} In our lab, students work in teams of between two and four collaborating both with each other and with others developing similar software. In addition there is personal interaction with students and teachers during the weekly goal setting and demonstrations.
    \item \textit{``At the same time students are ``scaffolded'' with material and tools to help them participate in activities that would  normally be beyond their abilities''} As will be described, extensive scaffolding is in ongoing development, in terms of narrative explanations, sample code and tutorials to practice on, and an extensive library of existing packages as part of the ROS Community and Ecosystem\cite{ROSCommunity}. 
    \item \textit{``Students create a set of tangible solutions to address the driving question, which are shared publicly and demonstrated to outsiders.''} Because our ``driving question'' spans multiple semesters, our tangible results, which take the form of presentations and demonstrations, will show off steps towards the goal.
\end{enumerate}

\subsection{Building on Project-Based Learning pedagogy}
As far as we know, we are the first to use the phrase "Multi-Semester, Multi-Cohort" so there will be no mention of it in the literature. But other than the phrase, there is certainly other relevant work that is quite instructive. 

One highly relevant example comes from ``Learning by Doing: Reflections of the Epics Program \cite{Epics}", Zoltowski and Oakes describe a ``multidisciplinary, vertically-integrated, student led, service-learning design course''. Here, students of all levels join and participate in multi-semester service projects built around a central framework, called ``Epics''. In this instance, students are working on projects on behalf of community partners who have their own time-lines. As a result projects can exceed a single semester, and even span multiple semesters. This approach is analogous to our Multi-Semester, Multi-Cohort model, except that in \textit{our course} there is but a single overarching objective. An interesting feature in the ``Epics" program is that the courses count for one half the normal course credits, which allows students to take the course more than once. This could be used to help create continuity from semester to semester, an issue that will be described below. 

Zoltowski and Oakes also mention the challenges of a multi-semester structure. One that we also experienced was the question of how information is conveyed from one semester (and in our case, one cohort as well) to the next. For ``Epics" the issue seemed to revolve around the technical means of sharing reports. Teams were sometimes reluctant to share publicly because they wanted to protect intellectual property. In the years since their work though it has become straightforward to share documents with fine grained access control (see Google documents, Dropbox and/or Github.) Zoltowski and Oakes also recognize the importance of encouraging each cohort to lay the groundwork for the next: ``Finally, attention to transitioning to the next semester is explicitly part of the course schedule and discourse.''

In ``Vertically Integrated Project (VIP) Programs: Multidisciplinary Projects with Homes in Any Discipline'' \cite{VIP}, Cullers, Hughes and Llewelly review a series of VIP programs. Their definition of VIP programs has a lot in common with ours but their motivations are different --- although quite relevant to our program. VIP ``unites undergraduate education and faculty research in a team based context.'' 

There is a specific emphasis on multi-year participation by students. In addition there is a focus on cost-savings, scalability and sustainability. These ideas are compelling ones for us to consider introducing into our approach. One key difference is that VIP programs seem to be strongly focused on research - that is providing a structure for undergraduates to participate over multiple years in research programs, essentially receiving credit instead of stipends. As our course is presently structured, students are effectively prevented from participating over multiple semester. The cited paper, in addition to introducing and defining the concept of the Vertically Integrated Project, also introduces the VIP Consortium \cite{VIPSite} and a series of programs and information about each one.

\subsection{Summary}
Figure \ref{fig:summary} is a summary of some of the key characteristics of the models alluded to above, meant simply as an easy way to compare the examples cited here. It is not the case that this is the only way to deploy each of these models.

\begin{table*}[h!]
    \begin{threeparttable}[b]
    \caption{Comparing Different Course Structures}
    	\begin{tabulary}
            {0.95\linewidth}{C|CCCCC} 
            \toprule
             & MSMC\tnote{1} & Traditional Course & Independent Study & Research Lab & VIP\tnote{2} \\
            \midrule
            Comp & credit & credit & credit & stipend & stipend \\
            Focus\tnote{3} & Applied & Both & Both & Research & Research \\
            Semesters & multiple & single & single & multiple & multiple \\
            Cohorts & multiple & single & multiple & single & single \\
            Structure\tnote{4} & team & either & single & either & team \\
            Freedom\tnote{5} & limited & none & full & limited & limited \\
            \bottomrule
    	\end{tabulary}
    	\begin{tablenotes}
    	    \item [1] MSMC: Multi Semester Multi Cohort1
    	    \item [2] VIP: Vertically Integrated Program
    	    \item [3] Focus: Used in Applied Computer Science or Research scenarios
    	    \item [4] Structure: Students work mostly in teams or on their own
    	    \item [5] Freedom: How much freedom do students have in choosing what they focus on
    	\end{tablenotes}
      	\label{fig:summary}
  	\end{threeparttable}        
\end{table*}

