\section{The Course}

We call our course ``Autonomous Robotics Lab". It is offered every semester, initially to a maximum of 12 students. As mentioned, in order to provide continuity and a sense of a greater purpose, we've chosen a ``major project" objective which was compelling to students, could not be solved in one semester, and provided the kind of learning opportunities that we were after. The goal we set for ourselves (the ``Campus Rover'' robot) is a partially unsolved problem with plenty of juicy sub-problems to keep us occupied.

\subsection{Who is admitted} As an experimental course we are being highly selective of the (up to 12) students who can take this course. Being experimental means a curriculum that is fluid with incomplete scaffolding and teaching staff who is also still learning. We administer this as follows:

We admit only Juniors, Seniors and Graduate students. The catalog states that permission from the instructor is required. Students are asked to fill out a short (Google) survey asking about grades received in key Computer Science courses, as well as a statement of qualification stating in their own words what previous experiences prepare them for the course. Finally, they are individually interviewed over email to determine that they are strong programmers, disciplined, motivated and with a demonstrated track record.

\subsection{Course Schedule} Our semesters are 13 weeks in length. During the first 4 semesters, students explore basic robotics concepts and theories, and at the same time learn the fundamentals of ``ROS'' through lectures and programming assignments. This is a very rapid pace for the material being covered and may prove to be too rapid. 

During a transition week, the students form into teams of 2 to 4 and decide on projects that will span the remainder of the semester. Students are guided to certain projects are offered the opportunity to propose their own. The  requirements for projects at this stage are that the projects have a clear role in the overall goal, that they are achievable in the remainder of the semester, and that the team can get excited about them.

During the remaining 7 weeks, the students have to get organized around their project, decide on tasks and assignments, and work through to their final deliverable. During this period we continue to have weekly lab meetings, now to review progress, see weekly demonstrations, and propose deliverables for the next week.

\subsection{Learning Objectives} Given that each semester would be different we had to have a clear sense of our learning objectives. In a general sense, the goal is to expose students to the problem solving learning that comes into play when working on a large software project with many moving parts.

Our objectives fall into two categories, Robotics and Software Engineering. Here they are, edited for length:

\begin{itemize}
\item Understand fundamentals of mobile autonomous robotics, and the notions of localization, navigation and planning, including being able to explain the SLAM algorithms.
\item Demonstrate the ability to design, implement and test programs written for ROS (Robot Operating System.) 
\item Be able to explain as well as implement the key primitives of ROS: nodes, topics, commands and services.
\item Be effective working in teams, designing new algorithms and solving problems of navigation and robotics, brainstorming, collaborating, implementing, testing and demonstrating the results of their work.
\item Demonstrate professional and agile software engineering processes, including writing elegant, readable, documented code, working in rapid iterations, each with a goal and a demo, and performing weekly stand-up\cite{standup} meetings.
\end{itemize}
